% SPDX-FileCopyrightText: 2023 Ricardo Guimarães <rfguimaraes0@gmail.com>
%
% SPDX-License-Identifier: Apache-2.0

\begin{rSection}{Experience}
    \expItem{Postdoctoral Research Fellow}{Dec 2020 \textendash{} Present}{\IIUiB, \UiB}{Bergen, Norway}[Full-time fixed-term]{%
        \begin{itemize}
            \item Published results on high-quality venues on Artificial Intelligence (AAAI 2023, NLDL 2023, JAIR (to appear)).
            \item Communicated results on international workshops.
            \item Planned, created material for, and delivered two courses.
            \item Co-supervised 2 master students and 2 PhD students.
            \item Co-organised a research school on Artificial Intelligence.
        \end{itemize}%
    }

    \expItem{Research Assistant}{Mar 2020 \textendash{} Nov 2020}{\SciTechUnibz, \Unibz}{Bozen-Bolzano, Italy}[Full-time fixed-term]{%
        \begin{itemize}
            \item Collaborated with international colleagues and presented research results at AAAI 2021.
        \end{itemize}%
    }

    \expItem{Academic Visitor}{Apr 2018 \textendash{} Jan 2019}{\IMGUoM, \UoM}{Manchester, UK}[Full-time internship]{%
        \begin{itemize}
            \item Published results of the collaboration in an international workshop on Ontology Modularity (WOMoCoE 2018).
            \item \href{https://bv.fapesp.br/en/bolsas/176114/improving-efficiency-of-belief-base-change-in-description-logics-with-modularity-in-ontologies/}{Funded by São Paulo Research Agency ({FAPESP})}.
        \end{itemize}%
    }

    \expItem{System Administrator}{Mar 2013 \textendash{} Feb 2015}{\RedeLinux, \IMEUSP, \USP}{São Paulo, Brazil}[Part-time internship]{%
        \begin{itemize}
            \item Maintained and developed the computer network that supports the institute's undergraduate students.
        \end{itemize}%
    }
\end{rSection}
